---
title: "A UN report on the relationship between GDP and life expectancy"
author: "Fred Feng"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)  # contains ggplot package
```

# Introduction

This report was prepared to the attention of the United Nations. 
It analyzes the relationship between *a country's GDP*, **its life expectancy** and *CO2 emissions*. 
Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.


```{r data, include=FALSE}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```

# Data Analysis

We evaluate the correlation between the GDP and the life expectancy.

```{r gdp_lifeexp_1997, echo=FALSE}

ggplot(data = gapminder_1997) +
  aes(x = `gdpPercap`) +
  labs(x = "GDP Per Capita") +
  aes(y = lifeExp) +
  labs(y = "Life Expectancy") +
  labs(title = "Do people in wealthy countries live longer?") +
  geom_point() +
  aes(color = continent) +
  scale_color_brewer(palette = "Set1") +
  aes(size = pop/10^6) +
  labs(size = "Population in millions") +
  aes(shape = continent)

```

